---
title: "Visualizing Model Fit for Old Faithful Eruption Data"
author: "Ryan Morton"
date: "April 24, 2017"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(caret)
library(randomForest)
library(plotly)
```

## The problem

* Comparing models is difficult for many users
* Direct comparison of models helps the decision making process
* Sometime the simplest model is just as good or better

## The solution

* [Final Project App](https://morton-analytics.shinyapps.io/data_products_final_project/)
* Put the models into the same application
* Seeing the models fitted to the data helps users understand what the model is doing
* Review goodness of fit and make your decision!

## Linear Model

```{r plotly_lm}
fit <- train(eruptions ~ waiting, data = faithful, method = "lm")
plot_ly(faithful, x = ~waiting, y = ~eruptions, type = "scatter", mode = "markers") %>%
       add_lines(x = ~waiting, y = fitted(fit)) %>%
       layout(showlegend = FALSE)
fit$results
```

## Randowm Forest Model

```{r plotly_rf, warning=FALSE}
fit <- train(eruptions ~ waiting, data = faithful, method = "rf")
plot_ly(faithful, x = ~waiting, y = ~eruptions, type = "scatter", mode = "markers") %>%
       add_lines(x = ~waiting, y = fitted(fit)) %>%
       layout(showlegend = FALSE)
fit$results
```